\documentclass{book}

\usepackage[dvipsnames, table]{xcolor}
%\usepackage{swrpg}
\usepackage{genesys}
\usepackage{hyperref}
%\geometry{paperheight=13in}
\usepackage{multicol}
\usepackage[noorphans,font=itshape,indentfirst=false,rightmargin=0pt]{quoting}

%\swrpgbackground
\newcommand{\xcnx}{\emph{No eXperience Required} }
\newcommand{\spa}{\hskip 0.3em }

% dice
\newcommand{\df}{\DifficultyDie }
\newcommand{\stb}{\SetbackDie }
\newcommand{\ch}{\ChallengeDie }
\newcommand{\abd}{\AbilityDie }
\newcommand{\bbb}{\BoostDie }
\newcommand{\pd}{\ProficiencyDie }

\renewcommand\Characteristics[6]{
\noindent\hfill
\charPart{BRAWN}{#1}\kern-.1em
\charPart{AGILITY}{#2}\kern-.1em
\charPart{INTELLECT}{#3}\kern-.1em
\charPart{CUNNING}{#4}\kern-.1em
\charPart{WILLPOWER}{#5}\kern-.1em
\charPart{PRESENCE}{#6}%
\hfill\null}

\newcommand{\npc}[9]{
    \begin{GenesysTable}{l} {\Large #1 } \end{GenesysTable} \\ %name
    \Characteristics{#2}{#3}{#4}{#5}{#6}{#7}\\
    \vskip -1em
    \Derived{Wounds}{#8}
    \Derived{Soak}{#9}
}
\newcommand{\npccontinued}[3]{
    \DerivedSplit{Defense}{#1}{#2}{Melee}{Ranged}\\ % defense
    \vskip -2.5em
    #3 %description, abilities, etc
}

\newcommand{\nemesis}[9]{
    \begin{GenesysTable}{l} {\Large #1 [Nemesis] } \end{GenesysTable} \\ %name
    \Characteristics{#2}{#3}{#4}{#5}{#6}{#7}\\
    \vskip -1em
    \Derived{Wounds}{#8}\hskip-.1em
    \Derived{Strain}{#9}\hskip-.1em
}
\newcommand{\nemesiscontinued}[4]{
    \Derived{Soak}{#1}\hskip-.1em
    \DerivedSplit{Defense}{#2}{#3}{Melee}{Ranged}\\ % defense
    \vskip -2.5em
    #4 %description, abilities, etc
}

\title{
    XCOM: No eXperience Required \\
A DiceyStories.com Genesys Adventure\\
}
\author{Author: Danielle Van Boxel}
\date{\today}

\newcommand{\prof}{
    {\color{brown} Prof allen}
}

\begin{document}
\maketitle


\begin{multicols*}{2}
\section{XCOM}

Hello, Commander.  The year is 1974, and aliens are secretly infiltrating our society.  We are activating XCOM, the eXterrestrial COmbat uniT.  What we need most is capable recruits, preferably with some experience resisting aliens.  Review this After Action Report to determine if the student group from Ares University should be an XCOM cell.

\section{Adventure Overview}

    The Player Characters (PCs) are graduate students at Ares University in the same research group, all supervised by \prof.  The lab is going together to a research conference in West Berlin.  While there, however, \prof asks that they recover critical research equipment from allegedly Nazi scientists.  The PCs discover, however, that the equipment, scientists, and even \prof are not entirely what they seem.

It is the height of the cold war.  Mistrust among governments, even neutral or supposedly allied ones, is rampant.  While the focus of this adventure is an \emph{alien} threat, the undercurrent of the setting reinforces \emph{human} tensions.

\emph{Goal}: Recover critical research equipment so it does not fall into the ``wrong'' hands.

\emph{Challenge}: \prof is actually an alien infiltrator.  She is using the PCs to steal a device that detects her alien form.  That ``device'' is actually an awoken psychic human who is a threat to alien infiltrators.

\subsection{Encounter List}
\begin{enumerate}
    \setlength\itemsep{-.8em}
    \item Dead student (information)
    \item Conference arrival (social)
    \item Biokinetic Waveform Analyzer (social/information)
    \item Crossing the border (social/stealth/physical)
    \item Facility infiltration (social/stealth)
    \item Entity extraction (stealth/combat)
    \item Research defense (social/combat)
    \item Aftermath
\end{enumerate}

\section{Dead Student}

Before even leaving for the conference, the PCs are discussing the recent den death of one member of \prof's research group, supposedly due to a medical condition.  Their passing was sudden, and no one seemed to be aware of a health problem before.  Each PC describes a detail about the now deceased student and how they knew each other.

    This encounter is primarily for the characters to establish Ares University and become more comfortable in the Cold War setting.  Each PC has an opportunity to use one skill to learn a little about what happened to their colleague before they head to the conference.  Here are just a few possibilities:

    \vspace{1em}
\begin{GenesysTable}{p{1.5in}p{2in}}
    Approach & \\
    \df\df \textbf{Charm} the Nurses Group & The paramedics who declared
    the student dead were not the usual crew.\\
    \df\df \textbf{Streetwise} at Hades Club & Rumor is that the student
    was poisoned.\\
        \df\df \textbf{Stealth} to check \prof's office & The student had a meeting with \prof just before being found dead.\\
    \df\df \textbf{Knowledge (Lore)} \hskip1em in Student's Room & ``Conspiracy Board'' suggests the student \prof had ties to the Nazis.\\
\end{GenesysTable}

\prof is an older woman, appearing to be in her seventies with light tan, almost leathery, skin.  She has one leg and uses a wheelchair.  Her slight central European accent and disability fuel rumors that she had been a Nazi scientist during the war but escaped to the Allies afterwards as part of Operation Paperclip.  She never directly answers questions about that time, and NPCs are polite enough not to ask.

If the PCs ask \prof about the student's death directly, she demurs and changes the subject, ``I understand this is hard on all of us.  But they would have wanted us to honor their memory by furthering our research.  Are you all set to travel to Berlin?''

\nemesis{Professor allen}{2}{4}{3}{3}{3}{2}{17}{15}
\nemesiscontinued{3}{1}{1}{
    \vspace{0.8em}
Reptilian alien masquerading as a frail professor.  Despite appearances, she is very swift and deadly.  In combat, she alternately spits acid and tongue yanks opponents.
\begin{GenesysTable}{rr}
    Skills &  \\
    Brawl 3 \pd\pd\abd   & Deception 3 \pd\pd\pd \\
    Coercion 2 \pd\pd\abd   & Discipline 1 \pd\abd\abd  \\
    Coordination 2 \pd\pd\abd\abd & Ranged (Light) 1 \pd\abd\abd\abd \\
\end{GenesysTable}\\
    \begin{GenesysTable}{lp{2in}}
    Abilities & \\
       Adversary 1 & Upgrade checks made against this NPC once. \\
        Acid Spit & 4 dmg, \textbf{Ranged (Light)} \pd\abd\abd\abd, Medium,
                Crit 4, Blast, Poison\\
        Tongue Pull/Bind & 4 dmg, \textbf{Brawl} \pd\pd\abd, Short, Entangle,
                 Yank (\df\df\df \textbf{Athletics/Coord} to resist 
                being pulled to Engaged) \\
\end{GenesysTable}\\
}

\prof is an alien Viper (i.e. snake person) posing as a scientist.  And she actually did infiltrate the Third Reich during the war.  She has no interest in that ideology or any other human political system.  Her one leg is a cover for her snake-like tail.  Alien genetic engineering is only so attuned to humans, so she takes care to keep it hidden.  Her name is always rendered in lowercase, as ``allen'' (i.e. very nearly ``alien''), though NPCs in-universe consider it an innocent quirk.

The dead student had discovered her alien identity, so she killed them with her venom and covered up the murder.  She is ruthless, but her mission is primarily providing intelligence on human societies and preventing human awareness of aliens.

\section{Conference Arrival}

After the brief discussion on campus, the PCs and \prof fly to the "Conference on Physical Psychology" held in West Berlin.  This is a very broad academic conference.  There are talks at a variety of technical levels and NPC researchers from many disciplines.  The PCs are staying at the hotel co-located with the conference.

After settling into their rooms (\df\df Social check if a PC wants to share a room with \prof), \prof speaks to them furtively,

\begin{quoting}
    I'm glad all of you are able to attend this conference, but I have small favor to ask.  Another research group is presenting ideas on a Biokinetic Waveform Analyzer.  This is an extremely dangerous technology, and they've secretly been working on a prototype.  We can't let this technology fall into the \emph{wrong hands}.  I need you to find and recover the prototype.
\end{quoting}

If the PCs ask questions, have them make a \df\df social check (e.g. \textbf{Charm}).  Even though this is against \prof, don't upgrade this check as she is expecting them to want a few more details.  She responds:

\begin{itemize}
    %\setlength\itemsep{-.5em}
    \item \Success ``The researchers experimenting with this technology are some of my...former colleagues during the war.  But they were true believers; the bastards will use it to raise a Fourth Reich!''
    \item \Advantage ``I represent an extranational organization, EXCALIBUR, dedicated to stopping threats worldwide.''
    \item \Triumph \prof advises that the Nazis scientists likely have a captive connected to their research.
    \item \Threat\Threat {}A nearby door creaks as footsteps quickly fade away.  Someone was eavesdropping on the conversation.  +\stb {}to a PC roll during the conference.
\end{itemize}

If not already mentioned, \prof thanks the PCs,

\vspace{-1em}
\begin{quoting}
    I appreciate your initiative in this matter.  I hate to have to involve you, but they know me well, and I'm not as spry as I once was.  You might start at the presentation tomorrow morning.  Your efforts will ensure the future of the planet.
\end{quoting}

\section{Biokinetic Waveform Analyzer}

As the conference proper begins, the PCs should try to learn more about the biokinetic waveform analyzer (BWA).  While attending the technical lecture is an obvious idea, there are several possible ways to learn more:

\newcolumn
\begin{GenesysTable}{p{1.5in}p{2in}}
    Approach & \\
        \ch\df \textbf{Knowledge (Science)} to understand talk & BWA can detect lifeforms and basic information about them.\\
    \df\df\df \textbf{Charm} to schmooze with academics & BWA has extreme computational cost, far beyond current capabilities. \\
    \df\df \textbf{Perception} to eavesdrop rumors & BWA prototype is in East Berlin and under armed guard.\\
    \ch\df \textbf{Skulduggery} to access back room of conference & Find device storage address, warehouse in East Berlin.  Soon to ship to Moscow.  \\
\end{GenesysTable}

The BWA talk, presented by Dr. Werner Strauss, is incredibly technical but mostly about applications rather than theory.  Some of the other academic attendees ask condescending questions pointing out that the ideas presented lack theoretical foundations.  The room is nearly full, though space is available to stand in the back.

If PCs generate {\Threat\Threat } in their investigation, they draw attention from the BWA ``research team''.  This team includes both scientific and military types.  They try to corner the PCs and scare them off further investigation.

If the PCs aren't able to find the location of the BWA nor the time-sensitive nature of the task, \prof informs them.  She explains that EXCALIBUR was able to come through with some critical intel.

\section{Crossing the border}

If time is limited, cut this scene and reframe the facility as actually being in \emph{West} Berlin.

Berlin wall border guards are notoriously strict, and Stasi informants watch everything in East Germany.  Crossing there and back is a challenge.  PCs start by gathering information about approaches to safely traverse the border.  Here are a few options with associated intel:

\df\df\stb \textbf{Perception} followed by \df\df \textbf{Stealth} to find smuggling tunnels or meet a ``Fluchthelfer'' who maintains one:
    \begin{itemize}
    \setlength\itemsep{-.5em}
        \item \Advantage\Advantage: A contact in East Germany is willing to help the PCs if they take them back with them to West Berlin.
        \item \Triumph: The Stasi don't know about this tunnel.  No \textbf{Stealth} check required on the other side.
        \item \Threat\Threat: The tunnel starts flooding during crossing, triggering an Easy [\df] Fear check.
        \item \Despair: Stasi demolitions teams collapose the tunnel just as PCs are exiting.  \df\df \textbf{Coordination} or \textbf{Vigilance} to avoid a Critical Injury.  And PCs have to find a different way back.
    \end{itemize}

\df\df \textbf{Streetwise} followed by \ch\df \textbf{Social} check to obtain forged papers allowing travel:
    \begin{itemize}
    \setlength\itemsep{-.5em}
    \item \Advantage\Advantage: One of the border guards is sympathetic.  Add \Success to the \textbf{Social} check.
        \item \Triumph:  The ``forged'' papers are actually legitimate and include protection against search and seizure.
        \item \Threat\Threat: Random inspections add \stb to the \textbf{Social} check to get past border guards.
        \item \Despair: The border is closed due to visiting dignitaries.  Upgrade the next check due to delays.
    \end{itemize}

Accumulating {\Threat\Threat\Threat } on these checks tips off Stasi informants to follow the PCs.  At an inconvenient moment during the warehouse encounter, they or other agents appear and complicate the situation further.

\section{Facility Infiltration}

Multiple lookouts patrol the warehouse holding the device.  A \df\df\stb \textbf{Perception} check reveals that these are low-level local hires, not the militant BWA personnel seen at the conference.  They won't fight PCs, but they will raise an alarm if the PCs fail to find a way through:

    \begin{GenesysTable}{p{1.9in}p{1.5in}}
    Approach & \\
        \df\df\stb \textbf{Stealth} + \df\df\textbf{Athletics} to scale an unwatched part of wall. & Leads to roof or window entrance.  +\bbb \textbf{Perception} inside.\\
        \df\df \textbf{Stealth} + \df\df\stb \textbf{Skulduggery} to sneakto side door and lockpick. & Leads to side entrance. +1 Ranged defense first round of combat.\\
        \df\df\df \textbf{Social} to lie/buy/bully way past guards. & Main entry and no chance to ambush/surveil BWA personnel. \\
\end{GenesysTable}

If the PCs gain entry without being seen, they observe parts of a private conversation.  A scientist is arguing with the militant \textbf{Viktor Roman}, an untrusting German, about the device.  Despite the risks, Viktor insists that ``sacrifices must be made to stamp out the snakes''.  In addition to Viktor, there are 2 minion groups of field scientists (2-3 each) and 1 to 2 additional military-style guards (use Viktor's stat block with all skills reduced to 1 rank and no special abilities).  Successful distractions set by the PCs earlier call some of these forces away, but Viktor and at least one scientist group are always in the warehouse.

Viktor and the scientists are remnants of the German group which first made contact with aliens as \prof alleged, but they cut all ties with ideological regimes.  They have a working BWA, a coffin-sized device capable of detecting space aliens.  And they are not keen on giving the BWA up, as they are preparing to deploy it in Moscow.  To fulfill \prof's request, however, the PCs must acquire the BWA and bring it back across the border.  This is the last chance before it moves irrevocably beyond the Iron Curtain.

(some classic XCOM art or 1970s berlin photo here)?

\newcolumn % TODO: verify needed
\npc{Viktor Roman [Rival]}{3}{3}{2}{3}{3}{3}{16}{4}
\npccontinued{1}{1}{
    \vspace{0.7em}
Leader of secretive anti-alien group developing the BWA.  He is willing to talk but will not give up his mission of deploying the BWA to Moscow.
\begin{GenesysTable}{rr}
    Skills &  \\
    Brawl 2 \pd\pd\abd &    Leadership 1 \pd\abd\abd\\
    Coercion 2 \pd\pd\abd & Ranged (Light) 2 \pd\pd\abd\\
    Discipline 2 \pd\pd\abd & Vigilance 1 \pd\abd\abd\\
\end{GenesysTable}
\begin{GenesysTable}{lp{2in}}
    Abilities & \\
       Adversary 1 & Upgrade all checks against this NPC once.\\
       Field Cmdr 1 & \df\df \textbf{Leadership} to give 3 allies
          an out-of-turn maneuver if they suffer 1 strain.\\
       Pistol & 6 dmg, Ranged (Light)\pd\pd\abd, Medium, Crit 3
\end{GenesysTable}
   }

\npc{Field Scientists [Minion]}{2}{2}{4}{2}{3}{2}{6}{3}
\npccontinued{0}{0}{
    \vspace{0.2em}
\begin{GenesysTable}{rr}
    Skills & \\
       Computers  & Knowledge (Lore)   \\
       Knowledge (Science)  & Mechanics  \\
\end{GenesysTable}
\begin{GenesysTable}{lp{2.2in}}
    Abilities & \\
       Expert Instruction & Assist maneuver upgrades the ability of the check once instead of adding \bbb.\\
       Pistol & 6 dmg, \textbf{Ranged (Light)} \abd\abd, Medium, Crit 3\\
\end{GenesysTable}
   }

Viktor and his security detail are resolute in their mission to take the BWA to Moscow and are willing to fight for it.  They do not attack on sight, but they are not swayable with social combat.  \Threat\Threat\Threat on checks in this scene triggers them to attack the PCs as the soldiers mark the PCs as a security risk.  The scientists care about preserving the BWA, not where it gets deployed.  They mostly assist and take cover during violence.  If Viktor and his soldiers fall in combat, all remaining scientists surrender.

\section{Entity Extraction}

What Viktor is loathe to reveal to the PCs is that \emph{the BWA contains a psychically active human being}, Edith.  Her capabilities circumvent the computational limitations  hinted at in the academic lecture.  She is in stasis within the device and clearly visible through a glass pane once PCs are standing next to the BWA.  She is connected to a variety of IVs and electrodes; it looks painful.

A quick \df\df\df\bbb \textbf{Coercion} or \df\df\df\bbb \textbf{Leadership} against a scientist will reveal that Edith is being used against her will.  She was originally a volunteer but never agreed to statis.  Viktor sent the only key to the device ahead to Moscow already, so opening it requires an alternative approach.

To free Edith, the PCs have to defeat the high security lock on the BWA, or they can smash the device and risk hurting her.  Scientists, if cowed, use \textbf{Expert Instruction} to assist by upgrading up to 2 PC checks.

Two separate successful checks are required to extract Edith without injury:

\df\df\df\stb \textbf{Skulduggery} or \df\df\df\df \textbf{Mechanics} to physically open the BWA:
    \begin{itemize}
    \setlength\itemsep{-.5em}
    \item \Failure: PCs have to try another method.  The medical extraction check is upgraded once for each failed check to open the BWA.  After 3 total failures, the device opens with a jolt of psionic energy, causing a Critical Injury to all PCs present.
        \item \Advantage\Advantage: The PCs recover data of recent readings showing alien activity at the conference.
        \item \Threat\Threat: Add \stb to the medical extraction check as there are more IVs than previously seen tethering Edith to the BWA.
        \item \Despair: Electrical current arcs across the device, jolting the PC and making them suffer a Critical Injury.
    \end{itemize}

\df\df\stb \textbf{Medicine} to safely unplug Edith from an array of tubes:
    \begin{itemize}
    \setlength\itemsep{-.5em}
        \item \Failure: Edith is deeply implanted into the device.  Forcibly cutting her out is possible, but she will suffer 2 Critical Injuries.
        \item \Advantage: Edith becomes alert and recognizes the PCs are trying to free her.
        \item \Threat\Threat: Edith becomes alert and misconstrues the PCs as further binding her.  \df\df\stb \textbf{Social} check to calm her.
        \item \Despair:  Edith's psychic abilities suddenly attack the PCs.  Each PC in short range must make \df\df\df \textbf{Vigilance} or \ch\df\df \textbf{Resilience} to avoid a Critical Injury.
    \end{itemize}

When Edith first comes to, she aggressively demands, ``Where are the snakes?'' as she eyes the PCs with suspicion.  Once out of the BWA and calm, however, Edith is generally disposed to help the PCs.  She freely travels with them to connect with \prof if asked.  The scientists, however, she despises, even if they helped the PCs.  They could have freed her earlier but did not; so she refuses to travel with them.  She is also somewhat mentally unbalanced by psionic conditioning.  She is more paranoid and aggressive than a typical soldier or spy.

(more cool art here?)
\newcolumn
\nemesis{Edith}{2}{2}{3}{2}{4}{2}{12}{13}
\nemesiscontinued{2}{0}{0}{
\vspace{0.2em}
\begin{GenesysTable}{rr}
    Skills & \\
    Coercion 1 \pd\abd\abd\abd & Psionics 2 \pd\pd\abd\abd\\
    Knowledge (Lore) 1 \pd\abd\abd & Vigilance 1 \pd\abd\abd\abd\\
    Perception 2 \pd\pd & \\
\end{GenesysTable}\\
    \begin{GenesysTable}{lp{2in}}
    Abilities & \\
        Detect Aliens & \df\df, \textbf{Psionics}\pd\pd\abd\abd, Medium, Spell\\
        Psionic Assault & 4 dmg, \df, \textbf{Psionics}\pd\pd\abd\abd, Short, Spell \\
        Stupefy & \df\df\df, \textbf{Psionics}\pd\pd\abd\abd, Short, Spell, stagger target \\
\end{GenesysTable}\\
}

The party has to sneak back into West Berlin, but this can be handled more succinctly than the earlier crossing.  If they had used official papers, they need to account for having an extra person (or the large BWA if she is still stuck inside).  If needed, Edith deploys her abilities to assist the return trip.

\section{Research Defense}

If Edith is awake when the PCs return to \prof, she has a severe reaction when within Medium range of the professor.  She quickly escalates from sneering, ``I smell a snake.'' to frenetically opening doors and gazing with wild eyes.  For narrative emphasis, this occurs on the other side of a hotel room door or other divider obscuring \prof as the immediate source of the reaction.  Being in such close proximity, Edith is unable to function clearly.  The PCs must restrain her or else she attacks the professor on sight.

If the PCs accuse \prof of being an alien, she becomes immediately hostile.  She gets two turns in a round (one in her initiative slot and one at the end of the round).  She takes distinct actions each turn of a round, like one spitting acid and another tongue binding.  Note that she is immune to her own acid.

Even if the PCs hand over Edith (who will resist if out of the device and alert), \prof still distrusts them as knowing too much.  They must pass a \ch\df\df\stb \textbf{Cool} or \textbf{Deception} check to play dumb.  Upgrade the difficulty if they rescued Edith but did not bring her to \prof:
    \begin{itemize}
    \setlength\itemsep{-.5em}
        \item \Failure: \prof decides the PCs know too much and attacks.
        \item \Advantage\Advantage: \prof is momentarily distracted and takes \stb on the initiative check.
        \item \Triumph: Edith or one of the PCs get a surprise attack on \prof
        \item \Threat\Threat: \prof also has an Alien Pistol (7 dmg, Medium, Crit 4, Burn 1).  It does not fire for humans if captured.
        \item \Despair:  Edith loses control and cannot tell friend from foe during the combat.
    \end{itemize}

If the PCs succeed in fooling \prof, they may choose to set a trap or string her along for more information.  Edith urges the PCs to capture \prof so they can interrogate her and learn more.

\section{Aftermath}

The night before the PCs fly home from Berlin, bright lights suddenly wake them. They see only dark silhouettes of a number of armed people on the other side of the lights.  The one nearest to the PCs flatly states, ``I understand you've seen some things not of this Earth.  We could use skills and resilience like yours...''.  The XCOM operative asks the PCs to keep an eye on \prof if she is still trusting, or take her into custody if she has been subdued.  This opens the adventure up into a longer campaign uncovering and dealing with alien threats at Ares University before formal induction as an XCOM cell.

Recommended XP: 10 XP for reaching the BWA/Edith.  10 XP for freeing her and confronting \prof.  Bonus 5 XP each if they befriend a BWA scientist or \emph{capture} \prof.

\section{Reference Material}

\begin{itemize}
    \setlength\itemsep{-.5em}
    \item Fluchthelfer - ``escape helpers'' who assisted refugees fleeing East Berlin.  \url{https://www.archives.gov/files/research/foreign-policy/cold-war/berlin-wall-1962-1987/dvd/pdfs/vingettes/4_V-10.pdf}
    \item Operation Paperclip - US effort to recruit German scientists in the immediate aftermath of WW2.  \url{https://wsmrmuseum.com/2022/03/28/operation-paperclip-at-fort-bliss-1945-1950/}
    \item XCOM - ``eXtraterrestrial COMbat'', a video game series featuring turn-based tactical sci-fi combat defending Earth from alien invasion.  \url{https://en.wikipedia.org/wiki/XCOM}
    \item Xenonauts - a ``spiritual successor'' video game series to the original 1990s XCOM games.  Set in the Cold War and with a lower human tech level.  \url{https://en.wikipedia.org/wiki/Xenonauts}
\end{itemize}


\end{multicols*}
\end{document}
